---
title: "Dose Calculator R Installation and Use Example"
author: "Test"
format: html
---

# Intro

This is a preliminary version of the R Dose calculator for cohorts based on
the ETAIN dose model. In this document, you find instructions on how to install
and run it on a small use example.

::: {.callout-important}
This project is in development and may not run perfectly. Do not use it for
analysis yet. Only use it for testing purposes.
::: 

The ETAIN Dose model will be updated in the future and so will this R package.
The number of input variables will increase to fine-tune the model. 

# Setup

```{r}
#| label: set_knitr_options
#| echo: False
#| eval: True
#| output: False
# Set project root directory as working directory
knitr::opts_knit$set(root.dir = here::here())
```

To install the Dose calculator, ask Irina (<irina.wipf@swisstph.ch>) to send you
the working version.

You will receive a file called ETAINDoseCalculator_0.1.0.tar.gz.

To install the Dose calculator, replace YOURPATH with the location of the file and run this command:

```{r}
#| label: load_emfdosecalculator
#| echo: True
#| eval: True
#| output: False
install.packages("U:/Projects/ETAINDoseCalculatoR/ETAINDoseCalculator_0.1.0.tar.gz", 
                 repos = NULL, 
                 type = "source")
```
Load the library:

```{r}
#| label: load_library
#| echo: True
#| eval: True
#| output: False
library(ETAINDoseCalculator)
```
To test if it worked, try this command:

```{r}
#| label: test-installation
#| echo: True
#| eval: True
#| output: False
?calculate_emf_doses()
```
You should see the (very short) documentation of the calculate_emf_doses() function pop up.

If it worked, you can load the example data set like this: 

```{r}
#| label: load_example_data
#| echo: True
#| eval: True
#| output: False
dataset_path <- ETAINDoseCalculator::example_data
```

Test if the dataset loaded correctly (you should see three example entries):
```{r}
head(example_data)
```

If successful, you can now calculate the doses for all samples:

```{r}
# | label: calculate_total_dose_all_samples
# Apply function row-wise
results <- calculate_emf_doses(data = example_data)
head(results)
```
You should see the original dataset with new columns, with the dose of each device and for brain and body.
