---
title: "ETAIN Dose Calculator R version"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ETAINDoseCalculatoR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(ETAINDoseCalculator)
```

## Overview

ETAINDoseCalculatoR is an R package designed to estimate personal radio-frequency electromagnetic field (RF-EMF) doses. It takes into account different device types and tissues, as well as exposure from far-field sources.

⚠️ *This package is currently under development. Calculations, functions and code structure are subject to change.*

## Goals

-  Provide reproducible RF-EMF dose estimates based on user input variables and pre-defined parameters.
-  Enable modular calculation of RF-EMF doses across tissues and exposure source types.
-  Support parameter overrides for additional flexibility.

## Theoretical Background

The calculations in this package are based on [INSERT REFERENCES]. They rely on scaling factors, device- and tissue-specific parameters, and user variables.

## Expected Input Data

The expected input is a csv file that contains ...

## Example Useage
### Basic Use
```{r}
# Example use
print("Insert use example here!")
```

### Customizing Parameters

By default, the ETAINDoseCalculatoR uses a pre-defined parameter list. However, it is possible to override these parameters. If you would like to do so, please follow these steps:
```{r}
# Example use
print("Insert use example here!")
```
### Generated output and documentation

Running the `{r}calculate_emf_doses()` function returns a data frame with a column containing the dose for each exposure source and tissue, as well as the total dose (which is simply the doses of each exposure source added together for a particular tissue).
```{r}
# Example use
print("Insert use example here!")
```
In addition, in the future `{r}calculate_emf_doses()` will also generate a log file that records the parameters used in the calculations and the number of missing variables that were replaced by default variables.

## Development Status

-  ✔️ Basic calculations implemented
-  ✔️ YAML parameter file generated
-  ⌛ Validation of calculations and unit testing in progress
-  ⌛ Customization of parameter file in progress
-  ❗ Default values not implemented yet
-  ❗ Output log file not implemented yet
-  ❗ Possible Shiny interface not implemented yet

## References

## Contributors and Acknowledgements
